\textbf{A Novel Experimental Paradigm Provides Evidence for a General Factor of Visual Illusion Sensitivity and Personality Correlates}

### 2022-10-20 submission/manuscript.Rmd
add coren lit

Despite strong theoretical foundations and hypotheses, the empirical evidence remains scarce, clouded by methodological hurdles. For instance, one key challenge can be found in the difficulty of adapting visual illusions to an experimental setting, which typically requires the controlled modulation of the specific variables of interest. Instead, existing studies typically use only one or a small subset of illusion types, with few contrasting conditions, restricting the findings' generalizability [@cretenoud2020illusions; @cretenoud2019; @bressan2021most]. Moreover, conventional paradigms often focus on the participants' subjective experience, by asking them the extent to which they perceive two identical targets as different [@lanyi2022can], or having them adjust the targets to perceptually match a reference stimulus [@mylniec2016; @grzeczkowski2018]. This reliance on meta-cognitive judgements about one's subjective experience likely distorts the measurand, limiting the ability to reliably obtain more direct and objective measures of illusion sensitivity [@skottun2014subjective].

>>>>

Despite strong theoretical foundations and hypotheses, the empirical evidence remains scarce, clouded by methodological hurdles. For instance, one key challenge can be found in the difficulty of adapting visual illusions to an experimental setting, which typically requires the controlled modulation of the specific variables of interest. Instead, existing studies typically use only one or a small subset of illusion types, with few contrasting conditions, restricting the findings' generalizability [@cretenoud2020illusions; @cretenoud2019; @bressan2021most]. Moreover, conventional paradigms often focus on the participants' subjective experience, by asking them the extent to which they perceive two identical targets as different [@lanyi2022can], having them estimate their perceptions of the targets' parametric properties (e.g., diameter of circular targets in the Ebbinghaus illusion) [@coren1976empirical] or having them adjust the targets to perceptually match a reference stimulus [@mylniec2016; @grzeczkowski2018]. This reliance on meta-cognitive judgements about one's subjective experience likely distorts the measurand, limiting the ability to reliably obtain more direct and objective measures of illusion sensitivity [@skottun2014subjective].
